---
title: "exp13bm11b_diff_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(forcats)
```

```{r}
source("./make_diff_plots.R")
source("./make_paper_plots.R")
```

# Effect of larger scenario space

This file creates plots of error diffs in exp13b vs exp11b on test data.
Since exp13b has more scenarios, we'd expect lower test errors (perhaps) and
the differences are exp13b - exp11b.


# exp11b vs exp13b

Is predictive accuracy impacted by the scenario grid size? I would think that
errors should be smaller for exp13b (larger scenario grid used to fit models.)

## Load results

```{r read_results}
exp11b_ldr_metrics <- read.csv("mm_output/exp11b/exp11b_ldr_metrics.csv", stringsAsFactors = TRUE)
exp11b_pp_metrics <- read.csv("mm_output/exp11b/exp11b_pp_metrics.csv", stringsAsFactors = TRUE)
exp11b_obs_metrics <- read.csv("mm_output/exp11b/exp11b_obs_metrics.csv", stringsAsFactors = TRUE)

exp13b_ldr_metrics <- read.csv("mm_output/exp13b/exp13b_ldr_metrics.csv", stringsAsFactors = TRUE)
exp13b_pp_metrics <- read.csv("mm_output/exp13b/exp13b_pp_metrics.csv", stringsAsFactors = TRUE)
exp13b_obs_metrics <- read.csv("mm_output/exp13b/exp13b_obs_metrics.csv", stringsAsFactors = TRUE)

# Combine
exp11b_metrics <- rbind(exp11b_ldr_metrics, exp11b_pp_metrics, exp11b_obs_metrics)
exp11b_metrics$exp <- 'exp11b'

exp13b_metrics <- rbind(exp13b_ldr_metrics, exp13b_pp_metrics, exp13b_obs_metrics)
exp13b_metrics$exp <- 'exp13b'

metrics <- rbind(exp11b_metrics, exp13b_metrics)

rm(exp11b_ldr_metrics, exp13b_ldr_metrics)
rm(exp11b_pp_metrics, exp13b_pp_metrics)
rm(exp11b_obs_metrics, exp13b_obs_metrics)
rm(exp11b_metrics, exp13b_metrics)
```

## Recode factors

```{r}
metrics$model <- recode_factor(metrics$model, 
                                      lassocv="LASSO",
                                      lm="LM",
                                      poly="POLY",
                                      rf="RF",
                                      nn="NNET",
                                      svr="SVR")


metrics$measure_nice <- recode_factor(metrics$measure, 
                                      occmean="mean occupancy",
                                      occp95="95%ile occupancy",
                                      probblocked="probability blocked",
                                      condmeantimeblocked="conditional mean time blocked")

metrics$unit_nice <- recode_factor(metrics$unit, 
                                      obs="Observation",
                                      ldr="LDR",
                                      pp="Postpartum"
                                      )

metrics$qdata_nice <- recode_factor(metrics$qdata, 
                                      noq="None",
                                      basicq="Basic",
                                      q="Advanced"
                                      )
```




## Aggregated performance over folds

To start, let's look at aggregated model performance over the 5 folds of the k-crossfold
validation process. A few notes:

* filtered out the pure queueing approximations for now (i.e. I'm only included fitted models)
* for occupancy statistics and conditional mean wait time we use MAPE
* for probability of blocking we use MAE (more relevant and easier to interpret)

### Overall aggregation

```{r aggregation}
metrics_agg <- metrics %>% 
  group_by(exp, unit, unit_nice, measure, measure_nice, qdata, model) %>% 
  summarize(
    train_mape = mean(train_mean_absolute_percentage_error),
    test_mape = mean(test_mean_absolute_percentage_error),
    train_mae = mean(train_mean_absolute_error),
    test_mae = mean(test_mean_absolute_error)
    
  )
```

## Compute differences

Now we need to split this dataframe back out into exp11b and exp13b versions to make it easy to subtract the 
error metrics.

```{r}
exp11b_metrics_agg <- metrics_agg %>% 
  filter(exp == 'exp11b')

exp13b_metrics_agg <- metrics_agg %>% 
  filter(exp == 'exp13b')
```

Now join the two identically structured tables.


```{r}
exp11b_exp13b_metrics_agg <- exp11b_metrics_agg %>% inner_join(exp13b_metrics_agg, by = c('unit', 'unit_nice', 'measure', 'measure_nice', 'qdata', 'model'),
                                 suffix = c('11', '13'))
```

Compute difference for mape

```{r}
exp11b_exp13b_metrics_agg <- exp11b_exp13b_metrics_agg %>% 
  mutate(
    test_mape_diff = test_mape13 - test_mape11,
    test_mae_diff = test_mae13 - test_mae11,
    train_mape_diff = train_mape13 - train_mape11,
    train_mae_diff = train_mae13 - train_mae11
  )
```

## Tables of sample size effect

```{r}
exp11b_exp13b_metrics_agg %>% 
  filter(measure == 'occmean') %>% 
  pivot_wider(names_from = model, values_from = test_mape_diff)
```



## Plots of sample size effect

Test manual plot

```{r ldr_occmean_mape}
plt_ldr_occmean_mape_diff <- exp11b_exp13b_metrics_agg %>% 
  filter(unit == 'ldr',
         qdata != 'onlyq', 
         model %in% c('LASSO', 'LM', 'POLY', 'NNET', 'RF', 'SVR'),
         measure == 'occmean') %>% 
  ggplot() +
  geom_point(aes(x=model, y=test_mape_diff, color=qdata, shape=qdata), 
             size=4) +
  labs(
    title = "LDR - mean occupancy",
    subtitle = "Impact of larger scenario grid",
    caption = NULL,
    tag = NULL,
    x = "Model type",
    y = "Change in MAPE",
    colour = "Feature set",
  ) + 
    scale_colour_discrete(name  ="Queueing features",
                            breaks=c("noq", "basicq", "q"),
                            labels=c("None", "Basic", "Advanced")) +
    scale_shape_discrete(name  ="Queueing features",
                           breaks=c("noq", "basicq", "q"),
                            labels=c("None", "Basic", "Advanced")) + 
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

plt_ldr_occmean_mape_diff
ggsave('mm_output/diff_plots/plt_ldr_occmean_mape_diff.png')
```
### LDR

```{r ldr_plots}
which_unit <- 'ldr'
which_subtitle <- ''

plot_height <- 4
plot_width <- 6

plt_ldr_occmean_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'LDR - mean occupancy',
                                       subtitle = which_subtitle)

ggsave(plt_ldr_occmean_mape_diff, filename = 'mm_output/diff_plots/exp13b_ldr_occmean_mape_diff.png',
       height = plot_height, width = plot_width)

plt_ldr_occp95_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'LDR - 95%ile occupancy',
                                      subtitle = which_subtitle)
ggsave(plt_ldr_occp95_mape_diff, filename = 'mm_output/diff_plots/exp13b_ldr_occp95_mape_diff.png',
       height = plot_height, width = plot_width)

plt_ldr_probblocked_mae_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                       measure = 'probblocked', error = 'mae',
                                       title = 'LDR - probability blocked',
                                       subtitle = which_subtitle)
ggsave(plt_ldr_probblocked_mae_diff, filename = 'mm_output/diff_plots/exp13b_ldr_probblocked_mae_diff.png',
       height = plot_height, width = plot_width)

plt_ldr_condmeantimeblocked_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                      measure = 'condmeantimeblocked', error = 'mape',
                                      title = 'LDR - conditional mean time blocked',
                                      subtitle = which_subtitle)
ggsave(plt_ldr_condmeantimeblocked_mape_diff, filename = 'mm_output/diff_plots/exp13b_ldr_condmeantimeblocked_mape_diff.png',
       height = plot_height, width = plot_width)
```

## PP

```{r pp_plots}
which_unit <- 'pp'
which_subtitle <- 'Impact of larger scenario grid'

plot_height <- 4
plot_width <- 6

plt_pp_occmean_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'PP - mean occupancy',
                                       subtitle = which_subtitle)
ggsave(plt_pp_occmean_mape_diff, filename = 'mm_output/diff_plots/exp13b_pp_occmean_mape_diff.png',
       height = plot_height, width = plot_width)

plt_pp_occp95_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'PP - 95%ile occupancy',
                                      subtitle = which_subtitle)
ggsave(plt_pp_occp95_mape_diff, filename = 'mm_output/diff_plots/exp13b_pp_occp95_mape_diff.png',
       height = plot_height, width = plot_width)


```

## OBS

```{r ldr_plots}
which_unit <- 'obs'
which_subtitle <- 'Impact of larger scenario grid'

plot_height <- 4
plot_width <- 6

plt_obs_occmean_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                       measure = 'occmean', error = 'mape',
                                       title = 'OBS - mean occupancy',
                                       subtitle = which_subtitle)
ggsave(plt_obs_occmean_mape_diff, filename = 'mm_output/diff_plots/exp13b_obs_occmean_mape_diff.png',
       height = plot_height, width = plot_width)

obs_occ95_note <- 'Note: Poly model with advanced queueing terms produces non-sensical results due to overfitting.'
plt_obs_occp95_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                      measure = 'occp95', error = 'mape',
                                      title = 'OBS - 95%ile occupancy',
                                      subtitle = which_subtitle, note = NULL,
                                     ylim_ub = 0.15)
ggsave(plt_obs_occp95_mape_diff, filename = 'mm_output/diff_plots/exp13b_obs_occp95_mape_diff.png',
       height = plot_height, width = plot_width)

plt_obs_probblocked_mae_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                       measure = 'probblocked', error = 'mae',
                                       title = 'OBS - probability blocked',
                                       subtitle = which_subtitle)
ggsave(plt_obs_probblocked_mae_diff, filename = 'mm_output/diff_plots/exp13b_obs_probblocked_mae_diff.png',
       height = plot_height, width = plot_width)

plt_obs_condmeantimeblocked_mape_diff <- mm_paper_error_diff_plot(exp11b_exp13b_metrics_agg, unit = which_unit,
                                      measure = 'condmeantimeblocked', error = 'mape',
                                      title = 'OBS - conditional mean time blocked',
                                      subtitle = which_subtitle)
ggsave(plt_obs_condmeantimeblocked_mape_diff, filename = 'mm_output/diff_plots/exp13b_obs_condmeantimeblocked_mape_diff.png',
       height = plot_height, width = plot_width)
```